Object naming is context dependent - A case study on testing linguistic hypotheses on real-world image corpora

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
adds images

\begin{figure}[t]
	\begin{center}
		\begin{minipage}{.35\textwidth}
			\includegraphics[scale=.15]{fig/graffig.pdf}
		\end{minipage}
		\begin{minipage}{.2\textwidth}
			\includegraphics[height=2cm,width=2.5cm]{fig/visual_genome_dogs.png}
		\end{minipage}
	\begin{minipage}{.2\textwidth}
		\includegraphics[height=2.5cm,width=2.5cm]{fig/flickr_1003163366_dog_boxes.jpg}
	\end{minipage}
	\begin{minipage}{.2\textwidth}
		\includegraphics[height=3cm,width=2.5cm]{fig/refcoco_2400_dog_boxes.jpg}
	\end{minipage}\vspace{-.7cm}\\
\begin{minipage}{.35\textwidth}
	...
\end{minipage}
\begin{minipage}{.2\textwidth}
	\tiny
	{\textsl{dalmatian, dog, heeler}}
\end{minipage}
\begin{minipage}{.2\textwidth}
	\textsl{\tiny dog}
\end{minipage}
\begin{minipage}{.2\textwidth}
	\tiny \textsl{dog}
\end{minipage}
	\end{center}
	\caption{Experimental and real-world visual scenes showing dogs (GET MORE IMAGES OF DOGS FROM VG???)}
	\label{fig:graf_genome}
\end{figure}

>>>>

\begin{figure}[t]
	\begin{center}
		\begin{minipage}{.35\textwidth}
			\includegraphics[scale=.15]{fig/graffig.jpg}
		\end{minipage}
		\begin{minipage}{.2\textwidth}
			\includegraphics[height=2cm,width=2.5cm]{fig/visual_genome_dogs.png}
		\end{minipage}
	\begin{minipage}{.2\textwidth}
		\includegraphics[height=2cm,width=2.5cm]{fig/flickr_1003163366_dog_boxes_crop.jpg}
	\end{minipage}
	\begin{minipage}{.2\textwidth}
		\includegraphics[height=2cm,width=2.5cm]{fig/refcoco_2400_dog_boxes_crop.jpg}
	\end{minipage}\vspace{-.7cm}\\
\begin{minipage}{.35\textwidth}
	...
\end{minipage}
\begin{minipage}{.2\textwidth}
	\tiny
	{\textsl{dalmatian, dog, heeler}}
\end{minipage}
\begin{minipage}{.2\textwidth}
	\textsl{\tiny dog}
\end{minipage}
\begin{minipage}{.2\textwidth}
	\tiny \textsl{dog}
\end{minipage}
	\end{center}
	\caption{Experimental and real-world visual scenes showing dogs (GET MORE IMAGES OF DOGS FROM VG???)}
	\label{fig:graf_genome}
\end{figure}
